The competing effects of the immune system and EMT on epithelial cancers

### 2019-04-19 Paper/Paper.tex
Continuing to try match Adam's

The effects of the immune system on a tumor can be broadly summarized into two modules.
The cytotoxic branch of the immune system, such as natural killer cells (NKs) and cytotoxic T cells (CTLs), seek out and lyse tumor cells.
Upon carrying out their effector functions, these cytotoxic cells lose efficacy or deactivate entirely\tcr{[REF]}.
The regulatory branch of the immune system, such as T regulatory cells (Tregs) and other factors, inhibits the effective functioning of the cytotoxic branch\cite{ruffell2010lymphocytes}.

>>>>

The effects of the immune system on a tumor can be broadly summarized into two modules. The cytotoxic branch of the immune system, such as natural killer cells (NKs) and cytotoxic T cells (CTLs), seek out and lyse tumor cells.
Upon carrying out their effector functions, these cytotoxic cells lose efficacy or deactivate entirely \cite{finn12_immunooncology-1}. The regulatory branch of the immune system (Tregs and other factors), inhibits the effective functioning of the cytotoxic branch \cite{ruffell2010lymphocytes}.
